Figures

### 2019-12-10 manuscript/figures.Rmd
tables and figures temporarily rendered separate from the manuscript
fixed descriptor contribution plots with patchwork updates
removed site location map

```{r siteLocations,fig.cap='Map showing locations of the nine sites used for collection of phenotypic descriptors.',fig.width=3,fig.height=5}
loadd(site_location_map)

print(site_location_map)
```

@@

descriptor_contribution_plots %>%
  wrap_plots()
```

>>>>

---
title: Figures
output: 
  pdf_document:
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

@@

descriptor_contribution_plots$a + descriptor_contribution_plots$b
```
